Market simulator

### 2020-09-28 analysis/05_market_simulator.Rmd
Create an export tab
Added Download Buttons into Export Tab

>>>>

### Export

```{r export}
# Render the organization configurations as a table
renderTable({
  org_choice = org_reactive()

  org_choice
})

# Download Button
downloadButton("download_org", label = "Download Organization Data")

downloadHandler(
  filename = function() {
    paste0("org_data_",Sys.time(),".csv")
  },
  content = function(file) {
    write.csv(org_reactive(), file)
  }
)

# Render the persona configurations as a table
renderTable({
  per_choice = per_reactive()

  per_choice
})

# Download Button
downloadButton("download_per", label = "Download Persona Data")

downloadHandler(
  filename = function() {
    paste0("persona_data_",Sys.time(),".csv")
  },
  content = function(file) {
    write.csv(per_reactive(), file)
  }
)

```
